Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-07-28 3dpas_intro.tex
adding a paragraph at the end of section 1 with info for the reader

>>>>

\textit{Guidance for the reader}: Readers who are generally knowledge about distributed
applications will likely feel comfortable reading the paper from start to end.
Readers with less distributed applications knowledge may prefer to read
\S\ref{sec:distdyndata} and \S\ref{sec:infrastructure} before \S\ref{sec:scenarios},
or might want to read \S\ref{sec:scenarios} first, but jump to \S\ref{sec:distdyndata} and \S\ref{sec:infrastructure} when they find terms which which they are unfamiliar.
Unfortunately, we do not feel that there is a single ordering of the information in this
paper that is best for all readers.
